
\section{3D Raster commands (r3.{*})}
\begin{description}
\item [{r3.colors}] Creates/modifies the color table associated with a
3D raster map.
\item [{r3.colors.out}] Exports the color table associated with a 3D raster
map.
\item [{r3.cross.rast}] Creates cross section 2D raster map from 3D raster
map based on 2D elevation map
\item [{r3.gwflow}] Numerical calculation program for transient, confined
groundwater flow in three dimensions.
\item [{r3.in.ascii}] Converts a 3D ASCII raster text file into a (binary)
3D raster map.
\item [{r3.in.bin}] Imports a binary raster file into a GRASS 3D raster
map.
\item [{r3.in.v5d}] Import 3-dimensional Vis5D files.
\item [{r3.in.xyz}] Create a 3D raster map from an assemblage of many coordinates
using univariate statistics
\item [{r3.info}] Outputs basic information about a user-specified 3D raster
map layer.
\item [{r3.mapcalc}] Raster map calculator.
\item [{r3.mask}] Establishes the current working 3D raster mask.
\item [{r3.mkdspf}] Creates a display file from an existing 3D raster map
according to specified threshold levels.
\item [{r3.neighbors}] Makes each voxel value a function of the values
assigned to the voxels around it, and stores new voxel values in an
output 3D raster map
\item [{r3.null}] Explicitly create the 3D NULL-value bitmap file.
\item [{r3.out.ascii}] Converts a 3D raster map layer into a ASCII text
file.
\item [{r3.out.bin}] Exports a GRASS 3D raster map to a binary array.
\item [{r3.out.netcdf}] Export a 3D raster map as netCDF file.
\item [{r3.out.v5d}] Exports GRASS 3D raster map to 3-dimensional Vis5D
file.
\item [{r3.out.vtk}] Converts 3D raster maps into the VTK-ASCII format.
\item [{r3.retile}] Retiles an existing 3D raster map with user defined
x, y and z tile size.
\item [{r3.stats}] Generates volume statistics for 3D raster maps.
\item [{r3.support}] Allows creation and/or modification of raster3d map
layer support files.
\item [{r3.timestamp}] Print/add/remove a timestamp for a 3D raster map
\item [{r3.to.rast}] Converts 3D raster maps to 2D raster maps
\item [{r3.univar}] Calculates univariate statistics from the non-null
cells of a 3D raster map.\end{description}

