
\section{Add-Ons}

\begin{lstlisting}
for D in *; do echo "${D}" |tr "\n" "|" && grep -A1 '#%module' ${D} |sed 's/#%module//g' |sed 's/#% description: //g'; don
\end{lstlisting}


d.correlate|

Prints a graph of the correlation between raster maps (in pairs).

d.out.file|

Saves the contents of the active display monitor to a graphics file.

d.polar|d.rast.edit|

Edits cell values in a raster map.

d.rast.leg|

Displays a raster map and its legend on a graphics window

d.redraw|

Redraws the content of currently selected monitor.

d.shadedmap|

Drapes a color raster over a shaded relief map.

d.to.rast|

Saves the contents of the active display monitor to a raster map.

d.vect.thematic|

Displays thematic vector map

d.what.rast|

Allows the user to interactively query raster map layers at user-selected
locations.

d.what.vect|

Allows the user to interactively query vector map layers at user-selected
locations.

db.dropcolumn|

Drops a column from selected attribute table.

db.droptable|

Drops an attribute table.

db.in.ogr|db.out.ogr|

Exports attribute tables into various formats.

db.test|

Test database driver, database must exist and set by db.connect.

db.univar|

Calculates univariate statistics on selected table column.

g.extension|

\#\% label: Maintains GRASS Addons extensions in local GRASS installation.

g.extension.all|

\#\% label: Rebuilds or removes all locally installed GRASS Addons
extensions.

g.gui.animation|

Tool for animating a series of raster and vector maps or a space time
raster or vector dataset.

g.gui.dbmgr|

Launches graphical attribute table manager.

g.gui.gcp|

Georectifies a map and allows to manage Ground Control Points.

g.gui.gmodeler|

\#\% label: Graphical Modeler.

g.gui.iclass|

\#\% label: Tool for supervised classification of imagery data.

g.gui.mapswipe|

Interactively compares two maps by swiping a visibility bar.

g.gui.psmap|

Tool for creating hardcopy map outputs.

g.gui.rlisetup|

Configuration tool for r.li modules.

g.gui.timeline|

Allows to compare temporal datasets by displaying their temporal extents
in a plot.

g.gui.vdigit|

Interactive editing and digitization of vector maps.

g.manual|

Displays the manual pages of GRASS modules.

i.colors.enhance|

Performs auto-balancing of colors for RGB images.

i.fusion.hpf|i.image.mosaic|

Mosaics several images and extends colormap.

i.in.spotvgt|

Imports SPOT VGT NDVI data into a raster map.

i.oif|i.pansharpen|i.spectral|i.tasscap|m.proj|

Converts coordinates from one projection to another (cs2cs frontend).

r.blend|

Blends color components of two raster maps by a given ratio.

r.buffer.lowmem|

\#\% label: Creates a raster map showing buffer zones surrounding
cells that contain non-NULL category values.

r.colors.stddev|

Sets color rules based on stddev from a raster map's mean value.

r.fillnulls|

Fills no-data areas in raster maps using spline interpolation.

r.grow|r.in.aster|r.in.srtm|r.in.wms|

Downloads and imports data from WMS/WMTS/NASA OnEarth server.

r.mask|

Creates a MASK for limiting raster operation.

r.out.xyz|

Exports a raster map to a text file as x,y,z values based on cell
centers.

r.pack|

Packs up a raster map and support files for copying.

r.plane|

Creates raster plane map given dip (inclination), aspect (azimuth)
and one point.

r.reclass.area|

Reclasses a raster map greater or less than user specified area size
(in hectares).

r.rgb|

Splits a raster map into red, green and blue maps.

r.tileset|

Produces tilings of the source projection for use in the destination
region and projection.

r.unpack|

Unpacks a raster map packed with r.pack.

r3.in.xyz|t.create|

Creates a space time dataset.

t.info|

Lists information about space time datasets and maps.

t.list|

Lists space time datasets and maps registered in the temporal database.

t.merge|

Merges several space time datasets into a single space time dataset.

t.rast.accdetect|

Detects accumulation patterns in temporally accumulated space time
raster datasets created by t.rast.accumulate.

t.rast.accumulate|

Computes cyclic accumulations of a space time raster dataset.

t.rast.aggregate|

Aggregates temporally the maps of a space time raster dataset by a
user defined granularity.

t.rast.aggregate.ds|

Aggregates data of an existing space time raster dataset using the
time intervals of a second space time dataset.

t.rast.colors|

Creates/modifies the color table associated with each raster map of
the space time raster dataset.

t.rast.export|

Exports space time raster dataset.

t.rast.extract|

Extracts a subset of a space time raster datasets.

t.rast.gapfill|

Replaces gaps in a space time raster dataset with interpolated raster
maps.

t.rast.import|

Imports space time raster dataset.

t.rast.list|

Lists registered maps of a space time raster dataset.

t.rast.mapcalc|

Performs spatio-temporal mapcalc expressions on temporally sampled
maps of space time raster datasets.

t.rast.neighbors|

Performs a neighborhood analysis for each map in a space time raster
dataset.

t.rast.out.vtk|

Exports space time raster dataset as VTK time series.

t.rast.series|

Performs different aggregation algorithms from r.series on all or
a subset of raster maps in a space time raster dataset.

t.rast.to.rast3|

Converts a space time raster dataset into a raster3d map.

t.rast.univar|

Calculates univariate statistics from the non-null cells for each
registered raster map of a space time raster dataset.

t.rast3d.extract|

Extracts a subset of a space time 3D raster dataset.

t.rast3d.list|

Lists registered maps of a space time raster3d dataset.

t.rast3d.mapcalc|

Performs r3.mapcalc expressions on maps of sampled space time 3D raster
datasets.

t.rast3d.univar|

Calculates univariate statistics from the non-null cells for each
registered raster3d map of a space time raster3d dataset.

t.register|

Registers raster, vector and raster3d maps in a space time datasets.

t.remove|

Removes space time datasets from temporal database.

t.rename|

Renames a space time dataset

t.sample|

Samples the input space time dataset(s) with a sample space time dataset
and print the result to stdout.

t.shift|

Shifts temporally the maps of a space time dataset.

t.snap|

Snaps temporally the maps of a space time dataset.

t.support|

Modifies the metadata of a space time dataset.

t.topology|

Lists temporal topology of a space time dataset.

t.unregister|

Unregisters raster, vector and raster3d maps from the temporal database
or a specific space time dataset.

t.vect.db.select|

Prints attributes of vector maps registered in a space time vector
dataset.

t.vect.export|

Exports a space time vector dataset as GRASS GIS specific archive
file.

t.vect.extract|

Extracts a subset of a space time vector dataset.

t.vect.import|

Imports a space time vector dataset from a GRASS GIS specific archive
file.

t.vect.list|

Lists registered maps of a space time vector dataset.

t.vect.observe.strds|

Observes specific locations in a space time raster dataset over a
period of time using vector points.

t.vect.univar|

Calculates univariate statistics of attributes for each registered
vector map of a space time vector dataset

t.vect.what.strds|

Stores raster map values at spatial and temporal positions of vector
points as vector attributes.

v.build.all|

Rebuilds topology on all vector maps in the current mapset.

v.centroids|v.class.ml|v.convert.all|

Converts all older versions of GRASS vector maps in current mapset
to current format.

v.db.addcolumn|

Adds one or more columns to the attribute table connected to a given
vector map.

v.db.addtable|

Creates and connects a new attribute table to a given layer of an
existing vector map.

v.db.dropcolumn|

Drops a column from the attribute table connected to a given vector
map.

v.db.droprow|

Removes a vector feature from a vector map through attribute selection.

v.db.droptable|v.db.join|

Joins a database table to a vector map table.

v.db.reconnect.all|

Reconnects attribute tables for all vector maps from the current mapset
to a new database.

v.db.renamecolumn|

Renames a column in the attribute table connected to a given vector
map.

v.db.univar|

Calculates univariate statistics on selected table column for a GRASS
vector map.

v.db.update|

Updates a column in the attribute table connected to a vector map.

v.dissolve|

Dissolves boundaries between adjacent areas sharing a common category
number or attribute.

v.in.e00|

Imports E00 file into a vector map.

v.in.geonames|

Imports geonames.org country files into a vector points map.

v.in.gns|

Imports US-NGA GEOnet Names Server (GNS) country files into a GRASS
vector points map.

v.in.lines|

Imports ASCII x,y{[},z{]} coordinates as a series of lines.

v.in.mapgen|

Imports Mapgen or Matlab-ASCII vector maps into GRASS.

v.in.wfs|v.krige|

Performs ordinary or block kriging for vector maps.

v.out.gps|v.pack|

Packs up a vector map and support files for copying.

v.rast.stats|

Calculates univariate statistics from a raster map based on a vector
map and uploads statistics to new attribute columns.

v.report|

Reports geometry statistics for vector maps.

v.to.lines|

Converts vector polygons or points to lines.

v.unpack|

Unpacks a vector map packed with v.pack.

v.what.vect|

Uploads vector values at positions of vector points to the table.

wxpyimgview|

Views BMP images from the PNG driver.
