
\section{Display commands (d.{*})}
\begin{description}
\item [{d.barscale}] Displays a barscale on the graphics monitor.
\item [{d.colorlist}] Output a list of all available display colors with
a configurable separator (default is comma).
\item [{d.colortable}] Displays the color table associated with a raster
map layer.
\item [{d.correlate}] Prints a graph of the correlation between raster
maps (in pairs).
\item [{d.erase}] Erases the contents of the active graphics display frame
with user defined color.
\item [{d.font}] Selects the font in which text will be displayed on the
user's graphics monitor.
\item [{d.fontlist}] Lists the available fonts.
\item [{d.geodesic}] Displays a geodesic line, tracing the shortest distance
between two geographic points along a great circle, in a longitude/latitude
data set.
\item [{d.graph}] Program for generating and displaying simple graphics
on the display monitor.
\item [{d.grid}] Overlays a user-specified grid in the active display frame
on the graphics monitor.
\item [{d.his}] Displays the result obtained by combining hue, intensity,
and saturation (his) values from user-specified input raster map layers.
\item [{d.histogram}] Displays a histogram in the form of a pie or bar
chart for a user-specified raster map.
\item [{d.info}] Displays information about the active display monitor.
\item [{d.labels}] Displays text labels (created with v.label) to the active
frame on the graphics monitor.
\item [{d.legend}] Displays a legend for a 2D or 3D raster map in the active
frame of the graphics monitor.
\item [{d.linegraph}] Generates and displays simple line graphs in the
active graphics monitor display frame.
\item [{d.mon}] Controls graphics display monitors from the command line.
\item [{d.northarrow}] Displays a north arrow on the graphics monitor.
\item [{d.out.file}] Saves the contents of the active display monitor to
a graphics file.
\item [{d.path}] Finds shortest path for selected starting and ending node.
\item [{d.polar}] Draws polar diagram of angle map such as aspect or flow
directions
\item [{d.profile}] Plots profile of a transect.
\item [{d.rast.arrow}] Draws arrows representing cell aspect direction
for a raster map containing aspect data.
\item [{d.rast.edit}] Edits cell values in a raster map.
\item [{d.rast}] Displays user-specified raster map in the active graphics
frame.
\item [{d.rast.leg}] Displays a raster map and its legend on a graphics
window
\item [{d.rast.num}] Overlays cell category values on a raster map displayed
in the active graphics frame.
\item [{d.redraw}] Redraws the content of currently selected monitor.
\item [{d.rgb}] Displays three user-specified raster maps as red, green,
and blue overlays in the active graphics frame.
\item [{d.rhumbline}] Displays the rhumbline joining two longitude/latitude
coordinates.
\item [{d.shadedmap}] Drapes a color raster over a shaded relief map.
\item [{d.text}] Draws text in the active display frame on the graphics
monitor using the current font.
\item [{d.thematic.area}] Displays a thematic vector area map in the active
frame on the graphics monitor.
\item [{d.title}] Create a TITLE for a raster map in a form suitable for
display with d.text.
\item [{d.to.rast}] Saves the contents of the active display monitor to
a raster map.
\item [{d.vect.chart}] Displays charts of vector data in the active frame
on the graphics monitor.
\item [{d.vect}] Displays user-specified vector map in the active graphics
frame.
\item [{d.vect.thematic}] Displays thematic vector map
\item [{d.what.rast}] Allows the user to interactively query raster map
layers at user-selected locations.
\item [{d.what.vect}] Allows the user to interactively query vector map
layers at user-selected locations.
\item [{d.where}] Identifies the geographic coordinates associated with
point locations given in display coordinates.\end{description}

