
\section{General commands (g.{*})}
\begin{description}
\item [{g.access}] Controls access to the current mapset for other users
on the system.
\item [{g.cairocomp}] Overlays multiple X Pixmaps.
\item [{g.copy}] Copies available data files in the current mapset search
path to the user's current mapset.
\item [{g.dirseps}] Internal GRASS utility for converting directory separator
characters.
\item [{g.extension.all}] Rebuilds or removes all locally installed GRASS
Addons extensions.
\item [{g.extension}] Maintains GRASS Addons extensions in local GRASS
installation.
\item [{g.filename}] Prints GRASS data base file names.
\item [{g.findetc}] Searches for GRASS support files.
\item [{g.findfile}] Searches for GRASS data base files and sets variables
for the shell.
\item [{g.gisenv}] Outputs and modifies the user's current GRASS variable
settings.
\item [{g.gui.animation}] Tool for animating a series of raster and vector
maps or a space time raster or vector dataset.
\item [{g.gui.dbmgr}] Launches graphical attribute table manager.
\item [{g.gui.gcp}] Georectifies a map and allows to manage Ground Control
Points.
\item [{g.gui.gmodeler}] Graphical Modeler.
\item [{g.gui}] Launches a GRASS graphical user interface (GUI) session.
\item [{g.gui.iclass}] Tool for supervised classification of imagery data.
\item [{g.gui.mapswipe}] Interactively compares two maps by swiping a visibility
bar.
\item [{g.gui.psmap}] Tool for creating hardcopy map outputs.
\item [{g.gui.rlisetup}] Configuration tool for r.li modules.
\item [{g.gui.timeline}] Allows to compare temporal datasets by displaying
their temporal extents in a plot.
\item [{g.gui.vdigit}] Interactive editing and digitization of vector maps.
\item [{g.list}] Lists available GRASS data base files of the user-specified
data type optionally using the search pattern.
\item [{g.manual}] Displays the manual pages of GRASS modules.
\item [{g.mapset}] Changes/reports current mapset.
\item [{g.mapsets}] Modifies/prints the user's current mapset search path.
\item [{g.message}] Prints a message, warning, progress info, or fatal
error in the GRASS way.
\item [{g.mkfontcap}] Generates the font configuration file by scanning
various directories for fonts.
\item [{g.parser}] Provides automated parser, GUI, and help support for
GRASS scipts.
\item [{g.pnmcomp}] Overlays multiple PPM image files.
\item [{g.ppmtopng}] Converts between PPM/PGM and PNG image formats.
\item [{g.proj}] Prints or modifies GRASS projection information files
(in various co-ordinate system descriptions).
\item [{g.region}] Manages the boundary definitions for the geographic
region.
\item [{g.remove}] Removes data base element files from the user's current
mapset using the search pattern.
\item [{g.rename}] Renames data base element files in the user's current
mapset.
\item [{g.tempfile}] Creates a temporary file and prints it's file name.
\item [{g.version}] Displays GRASS version info.\end{description}

