
\section{Imagery commands (i.{*})}
\begin{description}
\item [{i.albedo}] Computes broad band albedo from surface reflectance.
\item [{i.aster.toar}] Calculates Top of Atmosphere Radiance/Reflectance/Brightness
Temperature from ASTER DN.
\item [{i.atcorr}] Performs atmospheric correction using the 6S algorithm.
\item [{i.biomass}] Computes biomass growth, precursor of crop yield calculation.
\item [{i.cca}] Canonical components analysis (CCA) program for image processing.
\item [{i.cluster}] Generates spectral signatures for land cover types
in an image using a clustering algorithm.
\item [{i.colors.enhance}] Performs auto-balancing of colors for RGB images.
\item [{i.eb.eta}] Actual evapotranspiration for diurnal period (Bastiaanssen,
1995).
\item [{i.eb.evapfr}] Computes evaporative fraction (Bastiaanssen, 1995)
and root zone soil moisture (Makin, Molden and Bastiaanssen, 2001).
\item [{i.eb.hsebal01}] Computes sensible heat flux iteration SEBAL 01.
\item [{i.eb.netrad}] Net radiation approximation (Bastiaanssen, 1995).
\item [{i.eb.soilheatflux}] Soil heat flux approximation (Bastiaanssen,
1995).
\item [{i.emissivity}] Computes emissivity from NDVI, generic method for
sparse land.
\item [{i.evapo.mh}] Computes evapotranspiration calculation modified or
original Hargreaves formulation, 2001.
\item [{i.evapo.pm}] Computes potential evapotranspiration calculation
with hourly Penman-Monteith.
\item [{i.evapo.pt}] Computes evapotranspiration calculation Priestley
and Taylor formulation, 1972.
\item [{i.evapo.time}] Computes temporal integration of satellite ET actual
(ETa) following the daily ET reference (ETo) from meteorological station(s).
\item [{i.fft}] Fast Fourier Transform (FFT) for image processing.
\item [{i.gensig}] Generates statistics for i.maxlik from raster map.
\item [{i.gensigset}] Generates statistics for i.smap from raster map.
\item [{i.group}] Creates, edits, and lists groups of imagery data.
\item [{i.his.rgb}] Transforms raster maps from HIS (Hue-Intensity-Saturation)
color space to RGB (Red-Green-Blue) color space.
\item [{i.ifft}] Inverse Fast Fourier Transform (IFFT) for image processing.
\item [{i.image.mosaic}] Mosaics several images and extends colormap.
\item [{i.in.spotvgt}] Imports SPOT VGT NDVI data into a raster map.
\item [{i.landsat.acca}] Performs Landsat TM/ETM+ Automatic Cloud Cover
Assessment (ACCA).
\item [{i.landsat.toar}] Calculates top-of-atmosphere radiance or reflectance
and temperature for Landsat MSS/TM/ETM+/OLI
\item [{i.maxlik}] Classifies the cell spectral reflectances in imagery
data.
\item [{i.modis.qc}] Extracts quality control parameters from MODIS QC
layers.
\item [{i.oif}] Calculates Optimum-Index-Factor table for spectral bands
\item [{i.ortho.camera}] Select and modify the imagery group camera reference
file.
\item [{i.ortho.elev}] Select or modify the target elevation model.
\item [{i.ortho.rectify}] Orthorectifies an image by using the image to
photo coordinate transformation matrix.
\item [{i.pansharpen}] Image fusion algorithms to sharpen multispectral
with high-res panchromatic channels
\item [{i.pca}] Principal components analysis (PCA) for image processing.
\item [{i.rectify}] Rectifies an image by computing a coordinate transformation
for each pixel in the image based on the control points.
\item [{i.rgb.his}] Transforms raster maps from RGB (Red-Green-Blue) color
space to HIS (Hue-Intensity-Saturation) color space.
\item [{i.segment}] Identifies segments (objects) from imagery data.
\item [{i.smap}] Performs contextual image classification using sequential
maximum a posteriori (SMAP) estimation.
\item [{i.spectral}] Displays spectral response at user specified locations
in group or images.
\item [{i.target}] Targets an imagery group to a GRASS location and mapset.
\item [{i.tasscap}] Performs Tasseled Cap (Kauth Thomas) transformation.
\item [{i.topo.corr}] Computes topographic correction of reflectance.
\item [{i.vi}] Calculates different types of vegetation indices.
\item [{i.zc}] Zero-crossing \textquotedbl{}edge detection\textquotedbl{}
raster function for image processing.\end{description}

