
\section{Temporal commands (t.{*})}
\begin{description}
\item [{t.connect}] Prints/sets general temporal GIS database connection
for current mapset.
\item [{t.create}] Creates a space time dataset.
\item [{t.info}] Lists information about space time datasets and maps.
\item [{t.list}] Lists space time datasets and maps registered in the temporal
database.
\item [{t.merge}] Merges several space time datasets into a single space
time dataset.
\item [{t.rast.accdetect}] Detects accumulation patterns in temporally
accumulated space time raster datasets created by t.rast.accumulate.
\item [{t.rast.accumulate}] Computes cyclic accumulations of a space time
raster dataset.
\item [{t.rast.aggregate.ds}] Aggregates data of an existing space time
raster dataset using the time intervals of a second space time dataset.
\item [{t.rast.aggregate}] Aggregates temporally the maps of a space time
raster dataset by a user defined granularity.
\item [{t.rast.colors}] Creates/modifies the color table associated with
each raster map of the space time raster dataset.
\item [{t.rast.export}] Exports space time raster dataset.
\item [{t.rast.extract}] Extracts a subset of a space time raster datasets.
\item [{t.rast.gapfill}] Replaces gaps in a space time raster dataset with
interpolated raster maps.
\item [{t.rast.import}] Imports space time raster dataset.
\item [{t.rast.list}] Lists registered maps of a space time raster dataset.
\item [{t.rast.mapcalc}] Performs spatio-temporal mapcalc expressions on
temporally sampled maps of space time raster datasets.
\item [{t.rast.neighbors}] Performs a neighborhood analysis for each map
in a space time raster dataset.
\item [{t.rast.out.vtk}] Exports space time raster dataset as VTK time
series.
\item [{t.rast.series}] Performs different aggregation algorithms from
r.series on all or a subset of raster maps in a space time raster
dataset.
\item [{t.rast.to.rast3}] Converts a space time raster dataset into a raster3d
map.
\item [{t.rast.univar}] Calculates univariate statistics from the non-null
cells for each registered raster map of a space time raster dataset.
\item [{t.rast3d.extract}] Extracts a subset of a space time 3D raster
dataset.
\item [{t.rast3d.list}] Lists registered maps of a space time raster3d
dataset.
\item [{t.rast3d.mapcalc}] Performs r3.mapcalc expressions on maps of sampled
space time 3D raster datasets.
\item [{t.rast3d.univar}] Calculates univariate statistics from the non-null
cells for each registered raster3d map of a space time raster3d dataset.
\item [{t.register}] Registers raster, vector and raster3d maps in a space
time datasets.
\item [{t.remove}] Removes space time datasets from temporal database.
\item [{t.rename}] Renames a space time dataset
\item [{t.sample}] Samples the input space time dataset(s) with a sample
space time dataset and print the result to stdout.
\item [{t.shift}] Shifts temporally the maps of a space time dataset.
\item [{t.snap}] Snaps temporally the maps of a space time dataset.
\item [{t.support}] Modifies the metadata of a space time dataset.
\item [{t.topology}] Lists temporal topology of a space time dataset.
\item [{t.unregister}] Unregisters raster, vector and raster3d maps from
the temporal database or a specific space time dataset.
\item [{t.vect.db.select}] Prints attributes of vector maps registered
in a space time vector dataset.
\item [{t.vect.export}] Exports a space time vector dataset as GRASS GIS
specific archive file.
\item [{t.vect.extract}] Extracts a subset of a space time vector dataset.
\item [{t.vect.import}] Imports a space time vector dataset from a GRASS
GIS specific archive file.
\item [{t.vect.list}] Lists registered maps of a space time vector dataset.
\item [{t.vect.observe.strds}] Observes specific locations in a space time
raster dataset over a period of time using vector points.
\item [{t.vect.univar}] Calculates univariate statistics of attributes
for each registered vector map of a space time vector dataset
\item [{t.vect.what.strds}] Stores raster map values at spatial and temporal
positions of vector points as vector attributes.\end{description}

